---
title: "RATE Experiments Notebook - No X mean"
author: "Emily Winn"
output: pdf_document
---

# Introduction

This notebook is for visualizing the initial RATE experiments for the different interactions. These are the baby experiments and more complicated ones will follow.

In each experiment, we generate a data matrix $X$ which is $n=2000$ by $p=25$. We set the mixing coefficient between marginal and interactive effects to be $\rho = 0.5$ and $h^2 = 0.6$. In every scenario where there are marginal effects, we have the marginal effects coming equally from SNPS 23, 24, and 25. We consider three basic scenarios: 

* Same - In this situation, SNPs 23 and 24 each interact with 25. Thus all marginal and interactive effects come from these three SNPS.
* Diff - In this situation, SNPs 8 and 9 each interact with SNP 10. The interactive effects come from 8,9, and 10, while the marginal effects come from 23, 24, and 25
* Overlap - In this situation, SNPs 8 and 9 each interact with SNP 25. Thus SNP 25 contributes both interactive and marginal effects.
* Interact - 8 and 9 interact with 10, and 23 and 24 each interact with 25. There are no marginal effects.

For each of the generated data sets in each scenario, we run each of the following functions:

* `RATE` - otherwise referred to as "OG RATE", this is the original RATE function from Crawford et al 2018, and captures and ranks linear effects.
* `RATE_combo` - Captures the quadratic effects only, and does this by subtracting out the linear effects.
* `RATE_combo2` - Captures the quadratic effects without the removal of the linear effects.
* `RATE_combo` - Calculates both the linear and quadratic coefficients and adds them together before calculating effect sizes
* `RATE_MC` - First calculates a $g$ function for each SNP, then subtracts the predicted function $f$ and then runs RATE as usual.

The data parameters, the effect sizes, delta, and ESS for each RATE function, and the time to calculation is saved and stored in a series of lists, which we will load below in our analyses. All calculations were conducted on a 32 cores with 240 GB of memory.

# Updates from last time

* The `RATE_MC` function has been changed so that the second kernel for $g$ isn't centered and scaled (otherwise it just produces the same answers as the original `RATE` function). 
* The line about `Xmean` has been taken out of the data simulations.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(grid)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(crossval)
library(doParallel)
library("pracma")
cores = detectCores()
registerDoParallel(cores=cores)
```

```{r, echo = FALSE}
load('X:/RATEMC/RateSimExpReplicate/RATE_MA_same_ESAfastPar.Rdata')
load('X:/RATEMC/RateSimExpReplicate/RATE_MA_diff_ESAfastPar.Rdata')
load('X:/RATEMC/RateSimExpReplicate/RATE_interaction_ESAfastPar.Rdata')
load('X:/RATEMC/RateSimExpReplicate/RATE_MA_overlap_ESAfastPar.Rdata')
```

# Data Plots

## Effect Sizes

First code to put together data frames, which will be hidden in the output of the markdown file.

```{r, include=FALSE}
rate_types = c("RATE_OG", "RATE_quad", "RATE_quad2", "RATE_combo", "RATE_MC")
snps = paste("SNP",seq(25),sep="")
runs = paste("RATE", seq(100), sep="")

#Same first

SAME_OG_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_OG"]][["RATE"]]))))
SAME_quad_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_quad"]][["RATE"]]))))
SAME_quad2_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_quad2"]][["RATE"]]))))
SAME_combo_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_combo"]][["RATE"]]))))
SAME_MC_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_MC"]][["RATE"]]))))

#Diff next
DIFF_OG_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_OG"]][["RATE"]]))))
DIFF_quad_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_quad"]][["RATE"]]))))
DIFF_quad2_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_quad2"]][["RATE"]]))))
DIFF_combo_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_combo"]][["RATE"]]))))
DIFF_MC_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_MC"]][["RATE"]]))))

#Overlap after
OVERLAP_OG_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_OG"]][["RATE"]]))))
OVERLAP_quad_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_quad"]][["RATE"]]))))
OVERLAP_quad2_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_quad2"]][["RATE"]]))))
OVERLAP_combo_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_combo"]][["RATE"]]))))
OVERLAP_MC_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_MC"]][["RATE"]]))))

#Interact last
INTERACT_OG_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_OG"]][["RATE"]]))))
INTERACT_quad_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_quad"]][["RATE"]]))))
INTERACT_quad2_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_quad2"]][["RATE"]]))))
INTERACT_combo_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_combo"]][["RATE"]]))))
INTERACT_MC_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_MC"]][["RATE"]]))))


```

Now we want to plot stuff. There is a lot of code but you can skip all this to get to the graphs. The biggest thing to note is, regardless of scenario, it seems none of the functions were able to pick up on additive effects of 8, 9, or 10 when relevant. No idea why this is. `RATE_quad` and `RATE_quad2` also seem to be extra sensitive to noise.

```{r, echo = FALSE, plot=TRUE, fig.height=15, fig.width=20}

p_same <- SAME_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_diff <- DIFF_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_overlap <- OVERLAP_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_interact <- INTERACT_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

OGsame <- ggplot() + 
  geom_count(data=p_same, aes(x=SNPS, y = RATES), alpha=0.8, color="orange") +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Linear RATEs (same)")+
  geom_hline(yintercept=1/25, linetype="dashed",color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
  ylim(0,0.9)

OGdiff <- ggplot() +
  geom_count(data=p_diff, aes(x=SNPS,y=RATES), alpha=0.8, color="orange") +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Linear RATEs (diff)")+
  geom_hline(yintercept=1/25, linetype="dashed", color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
  ylim(0,0.9)
  
OGoverlap <- ggplot() + 
    geom_count(data=p_overlap, aes(x=SNPS,y=RATES),  alpha=0.8, color="orange") +
    scale_x_discrete(limits=snps) +
    theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
    ggtitle("GP Linear RATEs (overlap)")+
    geom_hline(yintercept=1/25, linetype="dashed", color="red",size=2)+
    theme_bw()+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
    ylim(0,0.9)

OGinteract <- ggplot() + 
    geom_count(data=p_interact, aes(x=SNPS,y=RATES),  alpha=0.8, color="orange") +
    scale_x_discrete(limits=snps) + 
    theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
    ggtitle("GP Linear RATEs (interact)") +
    geom_hline(yintercept=1/25, linetype="dashed", color="red",size=2)+
    theme_bw()+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
    ylim(0,0.9)

#plot the quad 

p_same <- SAME_quad_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_diff <- DIFF_quad_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_overlap <- OVERLAP_quad_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_interact <- INTERACT_quad_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

Quadsame <- ggplot() + 
  geom_count(data=p_same, aes(x=SNPS, y = RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("RATE Quad Effect Sizes (same)")+
  ylim(0,0.9)

Quaddiff <- ggplot()+
  geom_count(data=p_diff, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("RATE Quad Effect Sizes (diff)")+
  ylim(0,0.9)

Quadoverlap <- ggplot()+
  geom_count(data=p_overlap, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("RATE Quad Effect Sizes (overlap)")+
  geom_hline(yintercept=1/25, linetype="dashed")+
  ylim(0,0.9)

Quadinteract <- ggplot()+
  geom_count(data=p_interact, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("RATE Quad Effect Sizes (interact)")+
  ylim(0,0.9)

#plot the quad2

p_same <- SAME_quad2_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_diff <- DIFF_quad2_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_overlap <- OVERLAP_quad2_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_interact <- INTERACT_quad2_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")


Quad2same <- ggplot() + 
  geom_count(data=p_overlap, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Quad2 Effect Sizes (same)")+
  ylim(0,0.9)

Quad2diff <- ggplot()+
  geom_count(data=p_diff, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Quad2 Effect Sizes (diff)")+
  ylim(0,0.9)

Quad2overlap <- ggplot()+
  geom_count(data=p_overlap, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Quad2 Effect Sizes (overlap)")+
  ylim(0,0.9)

Quad2interact <- ggplot()+
  geom_count(data=p_interact, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Quad2 Effect Sizes (interact)")+
  ylim(0,0.9)

#plot the combo

p_same <- SAME_combo_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_diff <- DIFF_combo_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_overlap <- OVERLAP_combo_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_interact <- INTERACT_combo_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

Combosame <- ggplot() + 
  geom_count(data=p_same, aes(x=SNPS, y = RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Combo Effect Sizes (same)")+
  ylim(0,0.9)

Combodiff <- ggplot()+
  geom_count(data=p_diff, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Combo Effect Sizes (diff)")+
  ylim(0,0.9)

Combooverlap <- ggplot() + 
  geom_count(data=p_overlap, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Combo Effect Sizes (overlap)")+
  ylim(0,0.9)

Combointeract <- ggplot() + 
  geom_count(data=p_interact, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="right") +
  ggtitle("RATE Combo Effect Sizes (interact)")+
  ylim(0,0.9)

#plot the MC

p_same <- SAME_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_diff <- DIFF_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_overlap <- OVERLAP_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_interact <- INTERACT_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

MCsame <- ggplot() + 
  geom_count(data=p_same, aes(x=SNPS, y = RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (same)")+
  geom_hline(yintercept=1/25, linetype="dashed",color="red",size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
  ylim(0,0.9)

MCdiff <- ggplot() + 
  geom_count(data=p_diff, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (diff)")+
  geom_hline(yintercept=1/25, linetype="dashed", color="red",size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
  ylim(0,0.9)

MCoverlap <- ggplot() + 
  geom_count(data=p_overlap, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (overlap)")+
  geom_hline(yintercept=1/25, linetype="dashed",color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
  ylim(0,0.9)

MCinteract <- ggplot() + 
  geom_count(data=p_interact, aes(x=SNPS,y=RATES), alpha=0.8) +
  scale_x_discrete(limits=snps) + 
  #theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (interact)")+
  geom_hline(yintercept=1/25, linetype="dashed", color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none")+
  ylim(0,0.9)


#Combine all plots below in 2 x 3 matrix
#grid.arrange(OGsame, OGdiff, OGoverlap, OGinteract, Quadsame, Quaddiff, Quadoverlap, Quadinteract, Quad2same, Quad2diff, Quad2overlap, Quad2interact, Combosame, Combodiff, Combooverlap, Combointeract, MCsame, MCdiff, MCoverlap, MCinteract, nrow=5)
grid.arrange(OGsame, MCsame, OGdiff, MCdiff, OGoverlap, MCoverlap, OGinteract, MCinteract, nrow=4)
```
```{r, echo = FALSE, plot=TRUE, fig.height=15, fig.width=20}

p_same <- SAME_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_diff <- DIFF_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_overlap <- OVERLAP_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_interact <- INTERACT_OG_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

OGsame <- ggplot() + 
  geom_point(data=p_same, aes(x=SNPS, y = RATES, size=2),  color=same_scale) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Linear RATEs (same)")+
  geom_hline(yintercept=1/25, linetype="dashed",color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
  ylim(0,0.9)

OGdiff <- ggplot() +
  geom_point(data=p_diff, aes(x=SNPS, y = RATES, size=2),  color=diff_scale) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Linear RATEs (diff)")+
  geom_hline(yintercept=1/25, linetype="dashed", color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
  ylim(0,0.9)
  
OGoverlap <- ggplot() + 
    geom_point(data=p_overlap, aes(x=SNPS, y = RATES, size=2),  color=overlap_scale) +
    scale_x_discrete(limits=snps) +
    theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
    ggtitle("GP Linear RATEs (overlap)")+
    geom_hline(yintercept=1/25, linetype="dashed", color="red",size=2)+
    theme_bw()+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
    ylim(0,0.9)

OGinteract <- ggplot() + 
    geom_point(data=p_interact, aes(x=SNPS, y = RATES, size=2),  color=diff_scale) +
    scale_x_discrete(limits=snps) + 
    theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
    ggtitle("GP Linear RATEs (interact)") +
    geom_hline(yintercept=1/25, linetype="dashed", color="red",size=2)+
    theme_bw()+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
    ylim(0,0.9)

#plot the MC

p_same <- SAME_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_diff <- DIFF_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_overlap <- OVERLAP_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

p_interact <- INTERACT_MC_ESdf %>% select(snps) %>%
  pivot_longer(., cols = snps, names_to="SNPS", values_to = "RATES")

MCsame <- ggplot() + 
  geom_point(data=p_same, aes(x=SNPS, y = RATES, size=2),  color=same_scale) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (same)")+
  geom_hline(yintercept=1/25, linetype="dashed",color="red",size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
  ylim(0,0.9)

MCdiff <- ggplot() + 
  geom_point(data=p_diff, aes(x=SNPS, y = RATES, size=2),  color=diff_scale) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (diff)")+
  geom_hline(yintercept=1/25, linetype="dashed", color="red",size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
  ylim(0,0.9)

MCoverlap <- ggplot() + 
  geom_point(data=p_overlap, aes(x=SNPS, y = RATES, size=2),  color=overlap_scale) +
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (overlap)")+
  geom_hline(yintercept=1/25, linetype="dashed",color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
  ylim(0,0.9)

MCinteract <- ggplot() + 
  geom_point(data=p_interact, aes(x=SNPS, y = RATES, size=2),  color=diff_scale) +
  scale_x_discrete(limits=snps) + 
  #theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Nonlinear RATEs (interact)")+
  geom_hline(yintercept=1/25, linetype="dashed", color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
  ylim(0,0.9)


#Combine all plots below in 2 x 3 matrix
#grid.arrange(OGsame, OGdiff, OGoverlap, OGinteract, Quadsame, Quaddiff, Quadoverlap, Quadinteract, Quad2same, Quad2diff, Quad2overlap, Quad2interact, Combosame, Combodiff, Combooverlap, Combointeract, MCsame, MCdiff, MCoverlap, MCinteract, nrow=5)
grid.arrange(OGsame, MCsame, OGdiff, MCdiff, OGoverlap, MCoverlap, OGinteract, MCinteract, nrow=4, top=textGrob("RATE Data for Linear and Nonlinear Gaussian Processes Under Simulation Scenarios", gp=gpar(fontsize=24)))
```

```{r}
ggplot() + 
  geom_point(data=p_same, aes(x=SNPS, y = RATES, size=2), color=same_scale) +
  #scale_fill_manual(values = same_scale)+
  scale_x_discrete(limits=snps) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5), legend.position="none") +
  ggtitle("GP Linear RATEs (same)")+
  geom_hline(yintercept=1/25, linetype="dashed",color="red", size=2)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.text.x=element_blank())+
  #scale_color_manual(values = c("SNP23"="blue", "SNP24"="blue", "SNP25"="blue"))+          
  ylim(0,0.9)
```
## ROC's of RATE Values (plotted)

Here I will plot various ROC curves

```{r, echo=FALSE}
p_focus <- p_interact
snps_focus <- diff_snps
powers <- rep(0,100)
fdr <- rep(0,100)
for (i in 1:100){
  sig.rates <- p_focus[((i-1)*25+1):(i*25),] %>%filter(RATES>1/25)
  powers[i] = sum(sig.rates$SNPS%in%snps_focus)/length(snps_focus)
  fdr[i]=sum(sig.rates$SNPS%!in%snps_focus)/length(snps_focus)
}
mean(powers)
sd(powers)
mean(fdr)
sd(fdr)
```

```{r, echo=FALSE}
'%!in%' <- function(x,y)!('%in%'(x,y))
fdr <- rep(0,100)
for (i in 1:100){
  fdr[i]=sum(sig.rates$SNPS%!in%snps_focus)/length(snps_focus)
}

```
### Same

```{r, echo=FALSE}
same_snps = snps[23:25]
diff_snps = c(snps[8:10], snps[23:25])
interact_snps = diff_snps
overlap_snps = c(snps[8:10], snps[23:25])

### Define the Compute Power Function ###
compute.power <- function(pvals,SNPs){
  nsnps = length(pvals)
  Pos = SNPs #True Positive Set
  Negs = names(pvals)[which(names(pvals)%in%SNPs==FALSE)] #True Negative Set
  x = foreach(i = 1:nsnps)%dopar%{
    v = sort(pvals,decreasing = TRUE)[1:i] #Test Positives
    z = pvals[which(names(pvals)%in%names(v)==FALSE)] #Test Negatives
    
    TP = length(which(names(v)%in%Pos==TRUE))
    FP = length(which(names(v)%in%Pos==FALSE))
    TN = length(which(names(z)%in%Negs==TRUE))
    FN = length(which(names(z)%in%Negs==FALSE))
    
    TPR = TP/(TP+FN); FPR = FP/(FP+TN); FDR = FP/(FP+TP)
    c(TPR,FPR,FDR)
  }
  return(matrix(unlist(x),ncol = 3,byrow = TRUE))
}

power.sameOG = 0
for (i in 1:100){
  power.sameOG = power.sameOG + compute.power(RATE_MA_same[[2*i]]$RATE_OG$RATE, same_snps)
}
power.sameOG = power.sameOG/100

power.sameQuad = 0
for (i in 1:100){
  power.sameQuad = power.sameQuad + compute.power(RATE_MA_same[[2*i]]$RATE_quad$RATE, same_snps)
}
power.sameQuad = power.sameQuad/100

power.sameQuad2 = 0
for (i in 1:100){
  power.sameQuad2 = power.sameQuad2 + compute.power(RATE_MA_same[[2*i]]$RATE_quad2$RATE, same_snps)
}
power.sameQuad2 = power.sameQuad2/100

power.sameCombo = 0
for (i in 1:100){
  power.sameCombo = power.sameCombo + compute.power(RATE_MA_same[[2*i]]$RATE_combo$RATE, same_snps)
}
power.sameCombo = power.sameCombo/100

power.sameMC = 0
for (i in 1:100){
  power.sameMC = power.sameMC + compute.power(RATE_MA_same[[2*i]]$RATE_MC$RATE, same_snps)
}
power.sameMC = power.sameMC/100


```

ROC for same (SNPs 23, 24, 25 all have marginal effects, 23 and 25 and 24 and 25 are interactions.)
```{r, plot=TRUE}
PP = cbind(power.sameOG, power.sameQuad, power.sameQuad2, power.sameCombo, power.sameMC)
auc = c(trapz(PP[,2],PP[,1]),trapz(PP[,5],PP[,4]),trapz(PP[,8],PP[,7]),trapz(PP[,11],PP[,10]),trapz(PP[,14],PP[,13]))
m = paste(rate_types," (", format(round(auc,2),digits=2), ") ",sep = "")
#
same_pp = plot(PP[,2],PP[,1],type = "l",lty = 1, lwd = 3, col = "orange3", xlab = "False Positive Rate",ylab = "True Positive Rate", main="Power Curve (Same)", ylim = c(0,1),xlim = c(0,1),bty = "n")
#lines(PP[,5],PP[,4],type = "l",lty = 4, lwd = 3, col = "magenta")
#lines(PP[,8],PP[,7],type = "l",lty = 5, lwd = 3, col = "dark red")
#lines(PP[,11],PP[,10],type = "l",lty = 6, lwd = 3, col = "forest green")
lines(PP[,14],PP[,13],type = "l",lty = 2, lwd = 3, col = "blue")
#legend("bottomright",legend = m, lty =c(1,4,5,6,2), lwd = c(2,2,2,2,2),col = c("blue","magenta","dark red","forest green","orange3"),bty = "n",title = expression(bold("Method (AUC):")),title.adj = 0.15)
#abline(a=0, b=1,col="black",lwd = 2)
#dev.off()

```


### Different

ROC for different (marginal effects from snps 23, 24, 25, and interactions between 8 and 10 and 9 and 10).
```{r, plot=TRUE}
power.diffOG = 0
for (i in 1:100){
  power.diffOG = power.diffOG + compute.power(RATE_MA_diff[[2*i]]$RATE_OG$RATE, diff_snps)
}
power.diffOG = power.diffOG/100

power.diffQuad = 0
for (i in 1:100){
  power.diffQuad = power.diffQuad + compute.power(RATE_MA_diff[[2*i]]$RATE_quad$RATE, diff_snps)
}
power.diffQuad = power.diffQuad/100

power.diffQuad2 = 0
for (i in 1:100){
  power.diffQuad2 = power.diffQuad2 + compute.power(RATE_MA_diff[[2*i]]$RATE_quad2$RATE, diff_snps)
}
power.diffQuad2 = power.diffQuad2/100

power.diffCombo = 0
for (i in 1:100){
  power.diffCombo = power.diffCombo + compute.power(RATE_MA_diff[[2*i]]$RATE_combo$RATE, diff_snps)
}
power.diffCombo = power.diffCombo/100

power.diffMC = 0
for (i in 1:100){
  power.diffMC = power.diffMC + compute.power(RATE_MA_diff[[2*i]]$RATE_MC$RATE, diff_snps)
}
power.diffMC = power.diffMC/100

PP = cbind(power.diffOG, power.diffQuad, power.diffQuad2, power.diffCombo, power.diffMC)
auc = c(trapz(PP[,2],PP[,1]),trapz(PP[,5],PP[,4]),trapz(PP[,8],PP[,7]),trapz(PP[,11],PP[,10]),trapz(PP[,14],PP[,13]))
m = paste(rate_types," (", format(round(auc,2),digits=2), ") ",sep = "")
#
plot(PP[,2],PP[,1],type = "l",lty = 1, lwd = 3, col = "orange3", xlab = "False Positive Rate",ylab = "True Positive Rate", main="Power Curve (Different)", ylim = c(0,1),xlim = c(0,1),bty = "n")
#lines(PP[,5],PP[,4],type = "l",lty = 4, lwd = 3, col = "magenta")
#lines(PP[,8],PP[,7],type = "l",lty = 5, lwd = 3, col = "dark red")
#lines(PP[,11],PP[,10],type = "l",lty = 6, lwd = 3, col = "forest green")
lines(PP[,14],PP[,13],type = "l",lty = 2, lwd = 3, col = "blue")
#legend("bottomright",legend = m, lty =c(1,4,5,6,2), lwd = c(2,2,2,2,2),col = c("blue","magenta","dark red","forest green","orange3"),bty = "n",title = expression(bold("Method (AUC):")),title.adj = 0.15)
#abline(a=0, b=1,col="black",lwd = 2)
#dev.off()
```
### Overlap

ROC for overlap (marginal effects from snps 23, 24, 25, and interactions between 8 and 25 and 9 and 25).

```{r, plot=TRUE}
power.overlapOG = 0
for (i in 1:100){
  power.overlapOG = power.overlapOG + compute.power(RATE_MA_overlap[[2*i]]$RATE_OG$RATE, overlap_snps)
}
power.overlapOG = power.overlapOG/100

power.overlapQuad = 0
for (i in 1:100){
  power.overlapQuad = power.overlapQuad + compute.power(RATE_MA_overlap[[2*i]]$RATE_quad$RATE, overlap_snps)
}
power.overlapQuad = power.overlapQuad/100

power.overlapQuad2 = 0
for (i in 1:100){
  power.overlapQuad2 = power.overlapQuad2 + compute.power(RATE_MA_overlap[[2*i]]$RATE_quad2$RATE, overlap_snps)
}
power.overlapQuad2 = power.overlapQuad2/100

power.overlapCombo = 0
for (i in 1:100){
  power.overlapCombo = power.overlapCombo + compute.power(RATE_MA_overlap[[2*i]]$RATE_combo$RATE, overlap_snps)
}
power.overlapCombo = power.overlapCombo/100

power.overlapMC = 0
for (i in 1:100){
  power.overlapMC = power.overlapMC + compute.power(RATE_MA_overlap[[2*i]]$RATE_MC$RATE, overlap_snps)
}
power.overlapMC = power.overlapMC/100

PP = cbind(power.overlapOG, power.overlapQuad, power.overlapQuad2, power.overlapCombo, power.overlapMC)
auc = c(trapz(PP[,2],PP[,1]),trapz(PP[,5],PP[,4]),trapz(PP[,8],PP[,7]),trapz(PP[,11],PP[,10]),trapz(PP[,14],PP[,13]))
m = paste(rate_types," (", format(round(auc,2),digits=2), ") ",sep = "")
#
plot(PP[,2],PP[,1],type = "l",lty = 1, lwd = 3, col = "orange3", xlab = "False Positive Rate",ylab = "True Positive Rate", main = "Power Curve (Overlap)", ylim = c(0,1),xlim = c(0,1),bty = "n")
#lines(PP[,5],PP[,4],type = "l",lty = 4, lwd = 3, col = "magenta")
#lines(PP[,8],PP[,7],type = "l",lty = 5, lwd = 3, col = "dark red")
#lines(PP[,11],PP[,10],type = "l",lty = 6, lwd = 3, col = "forest green")
lines(PP[,14],PP[,13],type = "l",lty = 2, lwd = 3, col = "blue")
#legend("bottomright",legend = m, lty =c(1,4,5,6,2), lwd = c(2,2,2,2,2),col = c("blue","magenta","dark red","forest green","orange3"),bty = "n",title = expression(bold("Method (AUC):")),title.adj = 0.15)
#abline(a=0, b=1,col="black",lwd = 2)
#dev.off()

```

### Interact

ROC for interact (no marginal effects, 8 and 9 interact with 10, 23 and 24 interact with 25)

```{r, plot=TRUE}
power.interactOG = 0
for (i in 1:100){
  power.interactOG = power.interactOG + compute.power(RATE_MA_interact[[2*i]]$RATE_OG$RATE, interact_snps)
}
power.interactOG = power.interactOG/100

power.interactQuad = 0
for (i in 1:100){
  power.interactQuad = power.interactQuad + compute.power(RATE_MA_interact[[2*i]]$RATE_quad$RATE, interact_snps)
}
power.interactQuad = power.interactQuad/100

power.interactQuad2 = 0
for (i in 1:100){
  power.interactQuad2 = power.interactQuad2 + compute.power(RATE_MA_interact[[2*i]]$RATE_quad2$RATE, interact_snps)
}
power.interactQuad2 = power.interactQuad2/100

power.interactCombo = 0
for (i in 1:100){
  power.interactCombo = power.interactCombo + compute.power(RATE_MA_interact[[2*i]]$RATE_combo$RATE, interact_snps)
}
power.interactCombo = power.interactCombo/100

power.interactMC = 0
for (i in 1:100){
  power.interactMC = power.interactMC + compute.power(RATE_MA_interact[[2*i]]$RATE_MC$RATE, interact_snps)
}
power.interactMC = power.interactMC/100

PP = cbind(power.interactOG, power.interactQuad, power.interactQuad2, power.interactCombo, power.interactMC)
auc = c(trapz(PP[,2],PP[,1]),trapz(PP[,5],PP[,4]),trapz(PP[,8],PP[,7]),trapz(PP[,11],PP[,10]),trapz(PP[,14],PP[,13]))
m = paste(rate_types," (", format(round(auc,2),digits=2), ") ",sep = "")
#
plot(PP[,2],PP[,1],type = "l",lty = 1, lwd = 3, col = "orange3", xlab = "False Positive Rate", main="Power Curve (Interact)", ylab = "True Positive Rate", ylim = c(0,1),xlim = c(0,1),bty = "n")
#lines(PP[,5],PP[,4],type = "l",lty = 4, lwd = 3, col = "magenta")
#lines(PP[,8],PP[,7],type = "l",lty = 5, lwd = 3, col = "dark red")
#lines(PP[,11],PP[,10],type = "l",lty = 6, lwd = 3, col = "forest green")
lines(PP[,14],PP[,13],type = "l",lty = 2, lwd = 3, col = "blue")
#legend("bottomright",legend = m, lty =c(1,4,5,6,2), lwd = c(2,2,2,2,2),col = c("blue","magenta","dark red","forest green","orange3"),bty = "n",title = expression(bold("Method (AUC):")),title.adj = 0.15)
#abline(a=0, b=1,col="black",lwd = 2)
#dev.off()

```
# Time Trials
Need to extract the times for each thing and combine into data frames.

```{r}
#Same first

SAME_OG_Timedf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_OG"]][["Time"]]))))
SAME_quad_Timedf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_quad"]][["Time"]]))))
SAME_quad2_Timedf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_quad2"]][["Time"]]))))
SAME_combo_Timedf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_combo"]][["Time"]]))))
SAME_MC_Timedf <- as.data.frame(t(as.data.frame(map(RATE_MA_same[grep("RATE", names(RATE_MA_same))], ~.[["RATE_MC"]][["Time"]]))))

#Diff next
DIFF_OG_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_OG"]][["RATE"]]))))
DIFF_quad_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_quad"]][["RATE"]]))))
DIFF_quad2_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_quad2"]][["RATE"]]))))
DIFF_combo_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_combo"]][["RATE"]]))))
DIFF_MC_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_diff[grep("RATE", names(RATE_MA_diff))], ~.[["RATE_MC"]][["RATE"]]))))

#Overlap after
OVERLAP_OG_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_OG"]][["RATE"]]))))
OVERLAP_quad_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_quad"]][["RATE"]]))))
OVERLAP_quad2_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_quad2"]][["RATE"]]))))
OVERLAP_combo_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_combo"]][["RATE"]]))))
OVERLAP_MC_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_overlap[grep("RATE", names(RATE_MA_overlap))], ~.[["RATE_MC"]][["RATE"]]))))

#Interact last
INTERACT_OG_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_OG"]][["RATE"]]))))
INTERACT_quad_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_quad"]][["RATE"]]))))
INTERACT_quad2_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_quad2"]][["RATE"]]))))
INTERACT_combo_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_combo"]][["RATE"]]))))
INTERACT_MC_ESdf <- as.data.frame(t(as.data.frame(map(RATE_MA_interact[grep("RATE", names(RATE_MA_interact))], ~.[["RATE_MC"]][["RATE"]]))))


```


```{r}
plot(as.numeric(substr(SAME_OG_Timedf$V1, 1, nchar(SAME_OG_Timedf$V1)-5)), as.numeric(substr(SAME_MC_Timedf$V1, 1, nchar(SAME_MC_Timedf$V1)-5)), xlim=c(6,8), ylim=c(300,400))
```
